\cleardoublepage%
\chapter{\label{chap:bib_des}Few words on bibliography}%

The references come last. Using a reference manager while writing, e.g., Zotero, will allow the flexibility to change between different styles in the same manuscript, while streamlining organization, and facilitating transparency with your co-authors or supervisor. When you are using a reference manager, it will create the reference list at the end of the document though you will need to check each reference to make sure the information is complete. Update within the manager and reload the list if necessary.

\medskip

GHE uses APA 7th edition for our references. There are others, but this is one of the more common formats and is easy to follow. Please view the sample section below for a visual example of in-text citations. Citations should follow references to other author’s work, either in the form of a paraphrase, where you summarize their material in your own words, or a direct quote. Quotes should be used sparingly and very specifically. When you quote another author you need to include the relevant page number at the end of the citation. When you mention an author by name in the text, the citation appears after the name, and you omit their name in the citation, and only include the year.

\section{\label{sec:bib_des_format}Reference format}

References should be left-justified, with the first line hanging. This helps to identify individual references and keeps them from flowing into each other.

\section{\label{sec:bib_tools}Other tools}

You can proceed a citation with (see,) if you don’t want to reference a specific work, but want to point the reader towards specific reading (i.e. look here). (cf.) as a prefix to a citation, in APA, works as a compare, as if you want to draw comparisons between two texts.

\medskip

You can cite multiple authors at once, and it is often appropriate to do so, but do not be excessive. Concision is key, and that includes referencing. A wall of citations hurts the flow of manuscript. Gratuitous referencing is likewise bad. Unless it is a hallmark contribution within your field, or some grand theoretical piece that keeps getting built upon, I would seriously reflect on the necessity of including anything more than a decade old. Always think, what are the key, most topical sources to include? 
